Switch equivalence and weak prime domains for fusions

### 2023-12-15 fusione.tex

\begin{remark}\label{rem:lgt}
	Let $(\der{D}, \alpha, \omega)$ and $(\der{D}', \alpha', \omega')$ two composable decorated derivations   such that $\lgh(\der{D})=n$ and $\lgh(\der{D}')=m$.	 Then $(\der{D}*\omega^{-1}\cdot \alpha'*\der{D'}, \alpha, \omega')$ has length $n+m$.
\end{remark}
\iffalse 
\begin{proposition}\label{prop:ident}
Let $(\der{D}, \alpha, \omega)$ be a decorated derivation between $G$ and $H$ and  $(\der{D}',\alpha', \omega')$ be one between $G'$ and $H'$. Suppose, moreover that $G'$ and $H$ are isomorphic, so that $\pi(G')=\pi(H)$. Then the following hold true.
\begin{enumerate}
	\item If $\der{D}$ is the empty derivation, then
	\[(\der{D}, \alpha, \omega)\cdot (\der{D}',\alpha', \omega')\equiv_a (\der{D}',\alpha', \omega')\]
	\item  If $\der{D}'$ is the empty derivation, then
	\[(\der{D}, \alpha, \omega)\cdot (\der{D}',\alpha', \omega')\equiv_a (\der{D},\alpha, \omega)\]
\end{enumerate}
\end{proposition}
\begin{proof}
\begin{enumerate}
	\item 
	By \Cref{def:conc}, we have that 
	\[(\der{D}, \alpha, \omega)\cdot (\der{D}',\alpha', \omega')= (\der{D}', \alpha'\circ \omega^{-1}\circ \alpha, \omega')\]

	For every $X\in \Deltamin(\der{D'})$ we can define
	\[\phi_{X}:=\begin{cases}
		\alpha' \circ \alpha \circ \omega \circ (\alpha')^{-1} & X=G'\\
		\id{X} & \text{otherwise}
	\end{cases} \]
	Now, we can notice that $\phi_{G'_0}$ is the composition $\alpha'\circ (\alpha'\circ \omega^{-1}\circ \alpha)^{-1}$, giving us the triangle

\[\xymatrix@C=15pt{&\pi(G') \ar[dr]^{\alpha'} \ar[dl]_{\alpha'\circ \omega^{-1}\circ \alpha}\\ G'\ar[rr]_{\phi_{G'}} && G'} \]
To conclude the proof it is now enough to show the commutativity of 
	\[\xymatrix@C=40pt{G'&D'_0 \ar[r]^{g'_0} \ar[l]_{f'_0}&G'_{1}\\  L'_0 \ar[u]^{n'_0} \ar[d]_{n'_0}& K'_0 \ar[u]^{k'_0} \ar[d]_{k'_0} \ar[r]^{r'_0} \ar[l]_{l'_0} &R'_0\ar[u]^{h'_0} \ar[d]_{h'_0}\\G' \ar@/_.45cm/[uu]_(.35){\phi_{G'}}|\hole&D'_0\ar[l]^{f'_0}\ar@/_.45cm/[uu]_(.35){\id{D'_0}}|\hole \ar[r]_{g'_0}&G'_{1}\ar@/_.45cm/[uu]_{\id{G'_1}}}\]

\begin{remark}\label{rem:ident}Consider a decorated derivation $(\der{D}, \alpha, \omega)$ between $G$ and $H$ and another one $(\der{D}',\alpha', \omega')$ between $G'$ and $H'$. Suppose, moreover that $\pi(G')=\pi(H)$. By \Cref{rem:empty}, if $\der{D}$ is the empty derivation, so that $G=H$, then 
	\[(\der{D}, \alpha, \omega)\cdot (\der{D}',\alpha', \omega')= ((\omega \circ (\alpha')^{-1}) *\der{D}', \alpha, \omega')\]

Furthermore, we can notice that
\[(\der{D}', \alpha', \omega')\equiv_a ((\omega \circ (\alpha')^{-1}) *\der{D}', \alpha, \omega')\]	
Indeed, for every $X'\in \Deltamin(\der{D'})$ we can define
\[\phi_{X'}:=\begin{cases}
	(\alpha')^{-1} & X'=G'\\
	\id{X'} & \text{otherwise}
\end{cases} \]

Similarly, if $\lgh(\der{D}')=0$, implying $G'=H'$, we get
		\[(\der{D}, \alpha, \omega)\cdot (\der{D}',\alpha', \omega')=(\der{D}*\omega^{-1}, \alpha, \omega')\]

We can notice, moreover, that 
\[(\der{D}', \alpha', \omega')\equiv_a ((\omega \circ (\alpha')^{-1}) *\der{D}', \alpha, \omega') \qquad  (\der{D}, \alpha, \omega) \equiv_a (\der{D}*\omega^{-1}, \alpha, \omega')\] 	
Indeed,  for every $X'\in \Deltamin(\der{D'})$ and $X\in \Deltamin(\der{D})$ we can define
\[\phi_{X'}:=\begin{cases}
	(\alpha')^{-1} & X'=G'_{0}\\
	\id{X'} & \text{otherwise}
\end{cases} \qquad \phi_{X}:=\begin{cases}
\id{X} & \text{otherwise}\\
\omega^{-1} & X=H\\
\end{cases}\]

first of all notice that the triangles below commute.
\[\xymatrix@C=15pt{&\pi(G'_0) \ar[dr]^{\alpha'} \ar[dl]_{\alpha}&&& \pi(G) \ar[dr]^{\omega'} \ar[dl]_{\omega}\\ G\ar[rr]_{\phi} && G' &G' \ar[rr]_{\phi} && G' } \]

Furthermore, for every $X\in $ $i\in [0, \lgh(\der{D})]$

\end{remark}
\fi

The next proposition justifies the use of decorations, guaranteeing that concatenation of abstract decorated derivations is weel-defined.
\begin{lemma}\label{lem:conc}
	Given a decorated derivation $(\der{D}, \alpha, \omega)$  between $G$ and $H$ and  another one $(\der{E}, \beta, \xi)$ between $E$ and $K$ with $\pi(H)=\pi(E)$. If  $(\der{D}', \alpha', \omega')$ and $(\der{E}', \beta', \xi')$ are two other decorated derivations such that
	\[[\der{D}, \alpha, \omega]_a = [\der{D}', \alpha', \omega']_a \qquad [\der{D}, \beta, \xi]_a=[\der{E}', \beta', \xi']_a\]
	Then
	\[[(\der{D}, \alpha, \omega)\cdot (\der{E}, \beta, \xi)]_a=[(\der{D}', \alpha', \omega')\cdot (\der{E}', \beta', \xi')]_a\]
\end{lemma}

>>>>

\begin{remark}\label{rem:lgt}
	Let $(\der{D}, \alpha, \omega)$ and $(\der{D}', \alpha', \omega')$ two composable decorated derivations   such that $\lgh(\der{D})=n$ and $\lgh(\der{D}')=m$.	 Then $(\der{D}*\omega^{-1}\cdot \alpha'*\der{D'}, \alpha, \omega')$ has length $n+m$.
\end{remark}

The next proposition justifies the use of decorations, guaranteeing that concatenation of abstract decorated derivations is well-defined.
\begin{lemma}\label{lem:conc}
	Given a decorated derivation $(\der{D}, \alpha, \omega)$  between $G$ and $H$ and  another one $(\der{E}, \beta, \xi)$ between $E$ and $K$ with $\pi(H)=\pi(E)$. If  $(\der{D}', \alpha', \omega')$ and $(\der{E}', \beta', \xi')$ are two other decorated derivations such that
	\[[\der{D}, \alpha, \omega]_a = [\der{D}', \alpha', \omega']_a \qquad [\der{D}, \beta, \xi]_a=[\der{E}', \beta', \xi']_a\]
	Then
	\[[(\der{D}, \alpha, \omega)\cdot (\der{E}, \beta, \xi)]_a=[(\der{D}', \alpha', \omega')\cdot (\der{E}', \beta', \xi')]_a\]
\end{lemma}
